paper

### 2021-09-14 paper.Rmd
bbnb

```{r}
model1 <- brm(wt_14 ~ herbicide +
                (1|rep/location/year),
                  family = Beta(link = "logit", link_phi = "log"),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 15),
               prior = set_prior("student_t(0.1, 0.5, 2)", 
                                 class = "b"),
#                                 seed = 1235,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

@@

```{r}
model2 <- brm(wt_28 ~ herbicide +
                (1|rep/location/year),
                  family = Beta(link = "logit", link_phi = "log"),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999),
               prior = set_prior("student_t(0.1, 0.5, 2)", 
                                 class = "b"),
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

@@

@@

```{r}
epred1_1 %>% 
  bind_rows(epred2_2) %>% 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor")) -> epred_wt
```

```{r}
epred_wt %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean), 
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 465) +
  scale_color_brewer(palette = "Set1") +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11),
        legend.position = "none")

ggsave("figures/Figure 1.png", width = 9)
```

@@

```{r}
model4 <- brm(yield_kg ~ herbicide +
                (1|rep/location/year), 
                  family = gaussian(),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 15),
               prior = set_prior("normal(0, 2)", 
                                 class = "b"),
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

@@

@@

>>>>

```{r}
model1 <- brm(wt_14 ~ herbicide +
                (1|rep/location/year),
                  family = Beta(link = "logit", link_phi = "log"),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 11),
               prior = set_prior("student_t(0.1, 0.5, 8)", 
                                 class = "b"),
              seed = 1234,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

@@

```{r}
model2 <- brm(wt_28 ~ herbicide +
                (1|rep/location/year),
                  family = Beta(link = "logit", link_phi = "log"),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 11),
               prior = set_prior("student_t(0.1, 0.5, 8)", 
                                 class = "b"),
              seed = 1234,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

@@

```{r}
model3 <- brm(biomass_gm2 ~ herbicide +
                (1|rep/location/year), 
                  family = gaussian(),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 11),
               prior = set_prior("student_t(0.1, 1, 8)", 
                                 class = "b"),
              seed = 1234,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

```{r}
summary(model3)
```

```{r}
new_dt %>% 
  group_by(herbicide) %>% 
  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
            counts = sd(biomass_gm2, na.rm = TRUE))
```

```{r}
epred3 <- emmeans(model3, "herbicide", epred = TRUE, cont="pairwise")
```

@@

```{r}
epred1_1 %>% 
  bind_rows(epred2_2) %>% 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor")) %>% 
  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred_wt
```

```{r}
epred_wt %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean), 
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none")

ggsave("figures/Figure 2.png", width = 9)
```

@@

```{r}
model4 <- brm(yield_bu ~ herbicide +
                (1|rep/location/year), 
                  family = gaussian(),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 11),
               prior = set_prior("student_t(0.1, 2, 8)", 
                                 class = "b"),
              seed = 1234,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

@@

```{r}
new_dt %>% 
  group_by(herbicide) %>% 
  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
            counts = mean(counts_m2, na.rm = TRUE))
```

@@

```{r}
epred4$emmeans |> as_tibble() %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean), 
           y = emmean, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 size = 1.2) +
  coord_flip() +
  geom_text_repel(aes(label = round(emmean,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 465) +
  scale_color_brewer(palette = "Set1") +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11),
        legend.position = "none")

ggsave("figures/Figure 3.png", width = 9)
```
